---
title: "Analysis of results - T2SI vs predLMSIR"
author: "Cristina Gallego"
date: "August 25, 2017"
output: 
  html_document: 
    fig_caption: yes
    fig_width: 6
    keep_md: yes
    theme: cerulean
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, verbose = TRUE, warning=FALSE, message=FALSE, comment="")

options(width = 100)
setwd("Z:/Cristina/Section2/revision2-finalTreebased-boosting")
library(R.utils)
library(caret)
require(ggplot2)
library("RSQLite")
library(pROC)
library("Boruta")
require(data.table)
library(rpart)
library(rpart.plot)
library(R.utils)
require(ggplot2)
library(plyr)
library(pander)

source("functions.R")
source("functionsModels.R")
```

# Analysis of results by each fold
```{r process-cvks}
allcvauc_imgT1_total= c()
allcvauc_T1wT2w_total = c()
allcvauc_T2wpLMSIR_total= c()

## using 3Dtexture first + Boosting  
perfall_imgT1 = data.frame() 
perfall_imgT1T2 = data.frame() 
perfall_T2wpLMSIR = data.frame() 

varImpall_imgT1w_total = data.frame() 
varImpall_T1wT2w_total = data.frame() 
varImpall_T2wpLMSIR_total = data.frame() 

# perform k-fold-out
for(k in 1:10){  # 1:10f cv
  load(paste0("Outputs/T1T2imgvsT2wtextpredLMSIR_boost_addeddiagvalue_cv",k,".RData"))

  # append test results
  perfall_imgT1 = rbind(perfall_imgT1, perf_imgT1) 
  perfall_imgT1T2 = rbind(perfall_imgT1T2, perf_imgT1T2) 
  perfall_T2wpLMSIR = rbind(perfall_T2wpLMSIR, perf_T2wpLMSIR) 
  
  # append cv results
  allcvauc_imgT1_total = c(allcvauc_imgT1_total, rocperf_imgT1$auc)
  allcvauc_T1wT2w_total = c(allcvauc_T1wT2w_total, rocperf_imgT1T2$auc)
  allcvauc_T2wpLMSIR_total = c(allcvauc_T2wpLMSIR_total, rocperf_T2wpLMSIR$auc)

    
  # plot cv-heldout test cases
  par(mfrow=c(1,1))
  n=15
  colors = rainbow(n, s = 1, v = 1, start = 0, end = max(1, n - 1)/n, alpha = 1)
  # plot 1/4
  p1 = calcAUC_plot(perf_imgT1$obs, perf_imgT1$C, 
                             xptext=0.45, yptext=0.75 , 1, colors[2], atitle="")
  par(new=TRUE)
  p2 = calcAUC_plot(perf_imgT1T2$obs, perf_imgT1T2$C, 
                             xptext=0.55, yptext=0.65, 2, colors[9], atitle="")
  par(new=TRUE)
  p3 = calcAUC_plot(perf_T2wpLMSIR$obs, perf_T2wpLMSIR$C,
                             xptext=0.65, yptext=0.55, 3, colors[11], 
                    atitle=paste0("ROCs 10f-patient out cv test k-fold= ",k))
  
  legend("bottomright", 
          legend = c(paste0("T1w"),
                    paste0("T1w + T2wText + SI"),
                    paste0("T1w + T2wText + predLMSIR")),
         col = c(colors[2],colors[9],colors[11]), lwd = 2)

  
  ## process varImpts
  # returns the relative importance of each variable in the classification task.   
  # This measure takes into account the gain of the Gini index given by a variable in a tree and the weight of this tree.
  mostImp = treedata_imgT1$forest$importance[treedata_imgT1$forest$importance>0]
  varImp_imgT1w = data.frame(selfeat=names(mostImp),
                             gainGini=mostImp,
                             SelectedFeatureGroup="imgT1")
  row.names(varImp_imgT1w) = NULL
  
  # wimgT2
  mostImp = treedata_imgT1T2$forest$importance[treedata_imgT1T2$forest$importance>0]
  varImp_T2wmLMSIR = data.frame(selfeat=names(mostImp),
                             gainGini=mostImp,
                             SelectedFeatureGroup="imgT2")
  row.names(varImp_T2wmLMSIR) = NULL
  
  # wLMSIR
  mostImp = treedata_T2wpLMSIR$forest$importance[treedata_T2wpLMSIR$forest$importance>0]
  varImp_T2wpLMSIR = data.frame(selfeat=names(mostImp),
                             gainGini=mostImp,
                             SelectedFeatureGroup="T1+T2")
  row.names(varImp_T2wpLMSIR) = NULL
  
  ## group with all of the features spaces combined, most contributing T2w feature
  varImpall_imgT1w_total =  rbind(varImpall_imgT1w_total, cbind(varImp_imgT1w, kfcv=k) )
  varImpall_T1wT2w_total =  rbind(varImpall_T1wT2w_total, cbind(varImp_T2wmLMSIR, kfcv=k) )
  varImpall_T2wpLMSIR_total =  rbind(varImpall_T2wpLMSIR_total, cbind(varImp_T2wpLMSIR, kfcv=k) )
}

```

# Combine, pool data, and plot final results
```{r Summarize}
print(summary(allcvauc_imgT1))
print(summary(allcvauc_T1wT2w))
print(summary(allcvauc_T2wpLMSIR))

# boxplots of cv-performances
cvperfs = data.frame()
cvperfs = rbind(cvperfs, data.frame(cvAUC=allcvauc_imgT1, group="T1w"))
cvperfs = rbind(cvperfs, data.frame(cvAUC=allcvauc_T1wT2w, group="T1w+T2wText+T2w_SI"))
cvperfs = rbind(cvperfs, data.frame(cvAUC=allcvauc_T2wpLMSIR, group="T1w+T2wText+predictiveLMSIR"))
# find min
minAUC = min(cvperfs$cvAUC)

# plot
p <- ggplot(cvperfs, aes(factor(group), cvAUC))
p + geom_boxplot(aes(fill = factor(group)))


########### 
# plot pooled all cv-heldout test cases
par(mfrow=c(1,1))
n=15
colors = rainbow(n, s = 1, v = 1, start = 0, end = max(1, n - 1)/n, alpha = 1)
# plot 1/4
p1 = calcAUC_plot(perfall_imgT1$obs, perfall_imgT1$C, 
                           xptext=0.45, yptext=0.75 , 1, colors[2], atitle="")
par(new=TRUE)
p2 = calcAUC_plot(perfall_imgT1T2$obs, perfall_imgT1T2$C, 
                           xptext=0.55, yptext=0.65, 2, colors[9], atitle="")
par(new=TRUE)
p3 = calcAUC_plot(perfall_T2wpLMSIR$obs, perfall_T2wpLMSIR$C,
                           xptext=0.65, yptext=0.55, 3, colors[11], 
                  atitle="ROCs pooled heldout-patient across ALL folds")

legend("bottomright", 
       legend = c(paste0("T1w"),
                    paste0("T1w + T2wText + T2w_SI"),
                    paste0("T1w + T2wText + predictiveLMSIR")),
       col = c(colors[2],colors[9],colors[11]), lty=c(1,2,3), lwd = 2)


# find significants: only imgT1 vs. allT2
p1p2 = roc.test(p1$ROC, p2$ROC, method=c("bootstrap"), alternative = c("two.sided"), boot.stratified=TRUE)
print(p1p2)

# find significants: imgT1 vs wLMSIR
p1p3 = roc.test(p1$ROC, p3$ROC, method=c("bootstrap"), alternative = c("two.sided"), boot.stratified=TRUE)
print(p1p3)

# find significants: imgT1 vs wLMSIR
p2p3 = roc.test(p2$ROC, p3$ROC, method=c("bootstrap"), alternative = c("two.sided"), boot.stratified=TRUE)
print(p2p3)

```
 
 
# Adjust P-values for Multiple Comparisons

The adjustment methods include the Bonferroni correction ("bonferroni") in which the p-values are multiplied by the number of comparisons. Less conservative corrections are also included by Holm (1979) ("holm"), Hochberg (1988) ("hochberg"), Hommel (1988) ("hommel"), Benjamini & Hochberg (1995) ("BH" or its alias "fdr"), and Benjamini & Yekutieli (2001) ("BY"), respectively. 
 
The first four methods are designed to give strong control of the family-wise error rate. There seems no reason to use the unmodified Bonferroni correction because it is dominated by Holm's method, which is also valid under arbitrary assumptions.

```{r p-adjust}
pvals = c(p1p2$p.value, p1p3$p.value, p2p3$p.value)
p.adjust(pvals, method = "bonferroni", n = length(pvals))

```



# Analysis of the frequency of boosted trees used features
```{r featuressel, fig.height=24}
source("functions.R")

# plot features imgT1featsel wimgT2featsel wLMSIRfeatsel
## group with all of the features spaces combined, most contributing T2w feature
# pick frequency of 75% or higher as very common feature
dfimgT1 = data.frame(table(varImpall_imgT1w_total$selfeat))
dfimgT1$high = (dfimgT1$Freq>=0.75*max(varImpall_imgT1w_total$kfcv))*1
dfimgT1 = dfimgT1[order(dfimgT1$Freq, decreasing = TRUE),]

# prune only max frequencies, remove lesser frequencies
# with dictionary assign type of feature
dictimgT1 = feature_dictionary(imgT1train)
dfreqimgT1 = data.frame()
freqf = c()
for(di in 1:nrow(dfimgT1)){
  featname = as.character(dfimgT1[di,"Var1"])
  if(!(featname %in% freqf)){
    freqf = c(freqf, featname)
    dfreqimgT1 = rbind(dfreqimgT1, cbind(dfimgT1[di,],
                       typefeature=dictimgT1$fnnames[dictimgT1$fnnames$f==featname,"type"][1]))}}
print(dfreqimgT1)
  

#plot
ggplot(dfreqimgT1[dfreqimgT1$high==1,], aes(x=reorder(Var1, order(Freq, decreasing = TRUE)), y=Freq, fill=factor(typefeature))) + 
  geom_bar(stat = "identity") + coord_flip() +
  ggtitle("T1wonly ensembles: feature selection frequency") +
  labs(y="featsel frequency", x=" ") +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0))+
  theme(axis.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=16))

## varImpall_T1wT2w_total ########### 
# pick frequency of 75% or higher as very common feature
dfallT2 = data.frame(table(varImpall_T1wT2w_total$selfeat))
dfallT2$high = (dfallT2$Freq>=0.75*max(varImpall_T1wT2w_total$kfcv))*1
dfallT2 = dfallT2[order(dfallT2$Freq, decreasing = TRUE),]
print(dfallT2)

# prune only max frequencies, remove lesser frequencies
# with dictionary assign type of feature
dictimgT2 = feature_dictionary(imgT1T2)
dfreqimgT2 = data.frame()
freqf = c()
for(di in 1:nrow(dfallT2)){
  featname = as.character(dfallT2[di,"Var1"])
  if(!(featname %in% freqf)){
    freqf = c(freqf, featname)
    dfreqimgT2 = rbind(dfreqimgT2, cbind(dfallT2[di,],
                       typefeature=dictimgT2$fnnames[dictimgT2$fnnames$f==featname,"type"][1]))}}
print(dfreqimgT2)

#plot
ggplot(dfreqimgT2, aes(x=reorder(Var1, order(Freq, decreasing = TRUE)), y=Freq, fill=factor(typefeature))) + 
  geom_bar(stat = "identity") + coord_flip() +
  ggtitle("T1wonly ensembles: feature selection frequency") +
  labs(y="featsel frequency", x=" ") +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0))+
  theme(axis.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=16))



## varImpall_T2wpLMSIR_total ########### 
# pick frequency of 75% or higher as very common feature
dfwT1T2 = data.frame(table(varImpall_T2wpLMSIR_total$selfeat))
dfwT1T2$high = (dfwT1T2$Freq>=0.75*max(varImpall_T2wpLMSIR_total$kfcv))*1
dfwT1T2 = dfwT1T2[order(dfwT1T2$Freq, decreasing = TRUE),]
print(dfwT1T2)

# prune only max frequencies, remove lesser frequencies
# with dictionary assign type of feature
dictimgT1T2 = feature_dictionary(imgT2pLMSIR)
dfreqimgT1T2 = data.frame()
freqf = c()
for(di in 1:nrow(dfwT1T2)){
  featname = as.character(dfwT1T2[di,"Var1"])
  if(!(featname %in% freqf)){
    freqf = c(freqf, featname)
    dfreqimgT1T2 = rbind(dfreqimgT1T2, cbind(dfwT1T2[di,],
                       typefeature=dictimgT1T2$fnnames[dictimgT1T2$fnnames$f==featname,"type"][1]))}
  }
print(dfreqimgT1T2)

#plot
ggplot(dfreqimgT1T2[dfreqimgT1T2$high==1,], aes(x=reorder(Var1, order(Freq, decreasing = TRUE)), y=Freq, fill=factor(typefeature))) + 
  geom_bar(stat = "identity") + coord_flip() +
  ggtitle("T1w+T2wSI_noLMSIR ensembles: feature selection frequency") +
  labs(y="featsel frequency", x=" ") +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0))+
  theme(axis.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=16))

```


# now based on frequency of selecting a feature
```{r frequency-graphs}
# pick frequency of 75% or higher as very common feature
dfimgT1 = data.frame(table(varImpall_imgT1w_total$selfeat))
dfimgT1$high = (dfimgT1$Freq>=0.75*10)*3 + 
               (dfimgT1$Freq>=0.5*10 & dfimgT1$Freq<0.75*10)*2 + 
               (dfimgT1$Freq<0.5*10)*1
dfimgT1 = dfimgT1[order(dfimgT1$Freq, decreasing = TRUE),]

# with dictionary assign type of feature
dictimgT1 = feature_dictionary(imgT1train)
dfreqimgT1 = data.frame()
freqf = c()
for(di in 1:nrow(dfimgT1)){
  featname = as.character(dfimgT1[di,"Var1"])
  if(!(featname %in% freqf)){
    freqf = c(freqf, featname)
    dfreqimgT1 = rbind(dfreqimgT1, cbind(dfimgT1[di,],
                       typefeature=dictimgT1$fnnames[dictimgT1$fnnames$f==featname,"type"][1]))}}

T1w75orh =  dfreqimgT1[dfreqimgT1$high==3,]
T1w50to75 =  dfreqimgT1[dfreqimgT1$high==2,]
T1w25to50 =  dfreqimgT1[dfreqimgT1$high==1,]

# plot 2
# select freuqutnly selected features
maxFreq_dictT1w = summary(as.factor(dictimgT1$fnnames$type))
pander(maxFreq_dictT1w)

T1w75orhF = data.frame(featureGroup = names(summary(T1w75orh$typefeature)),
           freq = summary(T1w75orh$typefeature))
rownames(T1w75orhF)=NULL
T1w75orhF$flagSel = ">75%"
T1w50to75F = data.frame(featureGroup = names(summary(T1w50to75$typefeature)),
           freq = summary(T1w50to75$typefeature))
rownames(T1w50to75F)=NULL
T1w50to75F$flagSel = "50-75%"
T1w25to50F = data.frame(featureGroup = names(summary(T1w25to50$typefeature)),
           freq = summary(T1w25to50$typefeature))
rownames(T1w25to50F)=NULL
T1w25to50F$flagSel = "<50%"

allT1wFfreq = rbind(T1w75orhF, T1w50to75F, T1w25to50F)

maxFf= c()
for(i in 1:nrow(allT1wFfreq)){
  Ff = unname(maxFreq_dictT1w[names(maxFreq_dictT1w) == allT1wFfreq$featureGroup[i]])
  maxFf = c(maxFf, Ff)
}
allT1wFfreq$classifier = "T1wonly"

#plot +scale_fill_manual(values=c(p1,p2))
#p1<- barplot(1, angle = 45, density = 10, col = "black")
#p2<- barplot(1, angle = 145, density = 10, col = "grey")

# Get the positions of the labels
allT1wFfreq = ddply(allT1wFfreq, .(featureGroup), transform, pos = cumsum(freq) - 0.5*freq) 

labelsT1 = allT1wFfreq$freq
labelsT1[labelsT1==0]=""
allT1wFfreq$labels = labelsT1

ggplot(allT1wFfreq, aes(x=featureGroup, y=freq, fill=flagSel)) + 
  geom_bar(stat = "identity") + coord_flip()   +
  geom_text(aes(label = labels, y = pos), size = 3) +
  scale_fill_discrete(guide = guide_legend(title = "cv Selection\nfrequency")) +
  ggtitle("only T1w featsel") +
  labs(y="# features selected", x=" ") 


###########################################
# pick frequency of 75% or higher as very common feature
dfimgT1T2 = data.frame(table(varImpall_T2wpLMSIR_total$selfeat))
dfimgT1T2$high = (dfimgT1T2$Freq>=0.75*10)*3 + 
               (dfimgT1T2$Freq>=0.5*10 & dfimgT1T2$Freq<0.75*10)*2 + 
               (dfimgT1T2$Freq<0.5*10)*1
dfimgT1T2 = dfimgT1T2[order(dfimgT1T2$Freq, decreasing = TRUE),]

# with dictionary assign type of feature
dictimgT1T2 = feature_dictionary(imgT2pLMSIR)
dfreqimgT1T2 = data.frame()
freqf = c()
for(di in 1:nrow(dfimgT1T2)){
  featname = as.character(dfimgT1T2[di,"Var1"])
  if(!(featname %in% freqf)){
    freqf = c(freqf, featname)
    dfreqimgT1T2 = rbind(dfreqimgT1T2, cbind(dfimgT1T2[di,],
                       typefeature=dictimgT1T2$fnnames[dictimgT1T2$fnnames$f==featname,"type"][1]))}
  }

T1T2w75orh =  dfreqimgT1T2[dfreqimgT1T2$high==3,]
T1T2w50to75 =  dfreqimgT1T2[dfreqimgT1T2$high==2,]
T1T2w25to50 =  dfreqimgT1T2[dfreqimgT1T2$high==1,]

# plot 2
# select freuqutnly selected features
maxFreq_dictT1T2 = summary(as.factor(dictimgT1T2$fnnames$type))
pander(maxFreq_dictT1T2)

T1T2w75orhF = data.frame(featureGroup = names(summary(T1T2w75orh$typefeature)),
           freq = summary(T1T2w75orh$typefeature))
rownames(T1T2w75orhF)=NULL
T1T2w75orhF$flagSel = ">75%"
T1T2w50to75F = data.frame(featureGroup = names(summary(T1T2w50to75$typefeature)),
           freq = summary(T1T2w50to75$typefeature))
rownames(T1T2w50to75F)=NULL
T1T2w50to75F$flagSel = "50-75%"
T1T2w25to50F = data.frame(featureGroup = names(summary(T1T2w25to50$typefeature)),
           freq = summary(T1T2w25to50$typefeature))
rownames(T1T2w25to50F)=NULL
T1T2w25to50F$flagSel = "<50%"

allT1T2wFfreq = rbind(T1T2w75orhF, T1T2w50to75F, T1T2w25to50F)


maxFf= c()
for(i in 1:nrow(allT1T2wFfreq)){
  Ff = unname(maxFreq_dictT1T2[names(maxFreq_dictT1T2) == allT1T2wFfreq$featureGroup[i]])
  maxFf = c(maxFf, Ff)
}
allT1T2wFfreq$classifier = "T1w+T2w"

# finally plot
# Get the positions of the labels
allT1T2wFfreq = ddply(allT1T2wFfreq, .(featureGroup), transform, pos = cumsum(freq) - 0.5*freq)      

labels = allT1T2wFfreq$freq
labels[labels==0]=""
allT1T2wFfreq$labels = labels

ggplot(allT1T2wFfreq, aes(x=featureGroup, y=freq, fill=flagSel)) + 
  geom_bar(stat = "identity") + coord_flip()   +
  geom_text(aes(label = labels, y = pos), size = 3) +
  scale_fill_discrete(guide = guide_legend(title = "cv Selection\nfrequency")) +
  ggtitle("T1w +T2w_predicted LMSIR featsel") +
  labs(y="# features selected", x=" ") 


# plot combingin
allT1T2highF = rbind(allT1wFfreq, allT1T2wFfreq)
# plot
labelsT1T2 = allT1T2highF$freq
labelsT1T2[labelsT1T2==0]=""
allT1T2highF$labels = labelsT1T2

ggplot(allT1T2highF, aes(x=featureGroup, y=freq, fill=flagSel)) + 
  geom_bar(stat = "identity") + coord_flip()  +
  geom_text(aes(label = labels, y = pos), size = 3) +
  scale_fill_discrete(guide = guide_legend(title = "cv Selection\nfrequency")) +
  labs(y="# features selected", x=" ") + facet_grid(. ~ classifier)

#plot +scale_fill_manual(values=c(p1,p2))
#p1<- barplot(1, angle = 45, density = 10, col = "black")
#p2<- barplot(1, angle = 145, density = 10, col = "grey")

```

## Within relevant T2w features
```{r T2featsel}
# pick frequency of 75% or higher as very common feature
dfimgT2 = data.frame(table(varImpall_T2wpLMSIR_total$selfeat))
dfimgT2$high = (dfimgT2$Freq>=0.75*10)*3 + 
               (dfimgT2$Freq>=0.5*10 & dfimgT2$Freq<0.75*10)*2 + 
               (dfimgT2$Freq<0.5*10)*1
dfimgT2 = dfimgT2[order(dfimgT2$Freq, decreasing = TRUE),]

# with dictionary assign type of feature
dictimgT2 = feature_dictionary_typesT2(imgT2pLMSIR)
dfreqimgT2 = data.frame()
freqf = c()
for(di in 1:nrow(dfimgT2)){
  featname = as.character(dfimgT2[di,"Var1"])
  if(!(featname %in% freqf)){
    freqf = c(freqf, featname)
    if(any(dictimgT2$fnnames$f==featname)){
        dfreqimgT2 = rbind(dfreqimgT2, cbind(dfimgT2[di,],
                          typefeature=dictimgT2$fnnames[dictimgT2$fnnames$f==featname,"type"][1]))}}}

# only for selected T2w features
T2w75orh =  dfreqimgT2[dfreqimgT2$high==3,]
T2w50to75 =  dfreqimgT2[dfreqimgT2$high==2,]
T2w25to50 =  dfreqimgT2[dfreqimgT2$high==1,]

# plot 2
# select freuqutnly selected features
maxFreq_dictT2 = summary(as.factor(dictimgT2$fnnames$type))
pander(maxFreq_dictT2)

T2w75orhF = data.frame(featureGroup = names(summary(T2w75orh$typefeature)),
           freq = summary(T2w75orh$typefeature))
rownames(T2w75orhF)=NULL
T2w75orhF$flagSel = ">75%"
T2w50to75F = data.frame(featureGroup = names(summary(T2w50to75$typefeature)),
           freq = summary(T2w50to75$typefeature))
rownames(T2w50to75F)=NULL
T2w50to75F$flagSel = "50-75%"
T2w25to50F = data.frame(featureGroup = names(summary(T2w25to50$typefeature)),
           freq = summary(T2w25to50$typefeature))
rownames(T2w25to50F)=NULL
T2w25to50F$flagSel = "<50%"

allT2wFfreqpredicted = rbind(T2w75orhF, T2w50to75F, T2w25to50F)


maxFf= c()
for(i in 1:nrow(allT2wFfreqpredicted)){
  Ff = unname(maxFreq_dictT2[names(maxFreq_dictT2) == allT2wFfreqpredicted$featureGroup[i]])
  maxFf = c(maxFf, Ff)
}
allT2wFfreqpredicted$classifier = "selectedT2w"

# finally plot
# Get the positions of the labels
allT2wFfreqpredicted = ddply(allT2wFfreqpredicted, .(featureGroup), transform, pos = cumsum(freq) - 0.5*freq)

labelsT2 = allT2wFfreqpredicted$freq
labelsT2[labelsT2==0]=""
allT2wFfreqpredicted$labels = labelsT2

ggplot(allT2wFfreqpredicted, aes(x=featureGroup, y=freq, fill=flagSel)) + 
  geom_bar(stat = "identity") + coord_flip()  +
  geom_text(aes(label = labelsT2, y = pos), size = 3) +
  scale_fill_discrete(guide = guide_legend(title = "cv Selection\nfrequency")) +
  ggtitle("T1w+T2w_predicted LMSIR ensembles: T2w feature selection frequency") +
  labs(y="# features selected", x=" ") 


######################################
# pick frequency of 75% or higher as very common feature
dfimgT2 = data.frame(table(varImpall_T1wT2w_total$selfeat))
dfimgT2$high = (dfimgT2$Freq>=0.75*10)*3 + 
               (dfimgT2$Freq>=0.5*10 & dfimgT2$Freq<0.75*10)*2 + 
               (dfimgT2$Freq<0.5*10)*1
dfimgT2 = dfimgT2[order(dfimgT2$Freq, decreasing = TRUE),]

# with dictionary assign type of feature
dictimgT2 = feature_dictionary_typesT2(imgT1T2)
dfreqimgT2 = data.frame()
freqf = c()
for(di in 1:nrow(dfimgT2)){
  featname = as.character(dfimgT2[di,"Var1"])
  if(!(featname %in% freqf)){
    freqf = c(freqf, featname)
    if(any(dictimgT2$fnnames$f==featname)){
        dfreqimgT2 = rbind(dfreqimgT2, cbind(dfimgT2[di,],
                          typefeature=dictimgT2$fnnames[dictimgT2$fnnames$f==featname,"type"][1]))}}}

# only for selected T2w features
T2w75orh =  dfreqimgT2[dfreqimgT2$high==3,]
T2w50to75 =  dfreqimgT2[dfreqimgT2$high==2,]
T2w25to50 =  dfreqimgT2[dfreqimgT2$high==1,]

# plot 2
# select freuqutnly selected features
maxFreq_dictT2 = summary(as.factor(dictimgT2$fnnames$type))
pander(maxFreq_dictT2)

T2w75orhF = data.frame(featureGroup = names(summary(T2w75orh$typefeature)),
           freq = summary(T2w75orh$typefeature))
rownames(T2w75orhF)=NULL
T2w75orhF$flagSel = ">75%"
T2w50to75F = data.frame(featureGroup = names(summary(T2w50to75$typefeature)),
           freq = summary(T2w50to75$typefeature))
rownames(T2w50to75F)=NULL
T2w50to75F$flagSel = "50-75%"
T2w25to50F = data.frame(featureGroup = names(summary(T2w25to50$typefeature)),
           freq = summary(T2w25to50$typefeature))
rownames(T2w25to50F)=NULL
T2w25to50F$flagSel = "<50%"

allT2wFfreqmeasured = rbind(T2w75orhF, T2w50to75F, T2w25to50F)


maxFf= c()
for(i in 1:nrow(allT2wFfreqmeasured)){
  Ff = unname(maxFreq_dictT2[names(maxFreq_dictT2) == allT2wFfreqmeasured$featureGroup[i]])
  maxFf = c(maxFf, Ff)
}
allT2wFfreqmeasured$classifier = "selectedT2w"

# finally plot
# Get the positions of the labels
allT2wFfreqmeasured = ddply(allT2wFfreqmeasured, .(featureGroup), transform, pos = cumsum(freq) - 0.5*freq)

labelsT2 = allT2wFfreqmeasured$freq
labelsT2[labelsT2==0]=""
allT2wFfreqmeasured$labels = labelsT2

ggplot(allT2wFfreqmeasured, aes(x=featureGroup, y=freq, fill=flagSel)) + 
  geom_bar(stat = "identity") + coord_flip()  +
  geom_text(aes(label = labelsT2, y = pos), size = 3) +
  scale_fill_discrete(guide = guide_legend(title = "cv Selection\nfrequency")) +
  ggtitle("T1w+T2w_measure LMSIR ensembles: T2w feature selection frequency") +
  labs(y="# features selected", x=" ") 
```
               

```{r save}
save.image("Outputs/T2SIvspredLMSIR_summaryResults.RData")
```

